\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-07-28 analysis/paper/paper.Rmd
extended figure width to match text

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE, 
  comment = "#>",
  fig.path = "../figures/"
)
options(kableExtra.latex.load_packages = FALSE)
library(casebase)
library(colorspace)
library(cowplot)
library(data.table)
library(glmnet)
library(kableExtra)
library(magrittr)
library(pracma)
library(flexsurv) # for fitting gompertz AFT
library(prodlim)
library(riskRegression)
library(splines)
library(survival)
library(tibble)
library(visreg)
library(lubridate)
library(tidyverse)
library(scales)
options(digits = 2, scipen = 999)
# set the seed for reproducible output
set.seed(1234)

eval_introduction <- TRUE
eval_theory <- TRUE
eval_implementation <- TRUE
eval_cs1 <- T
eval_cs2 <- T
eval_cs3 <- TRUE
eval_cs4 <- T
eval_colophon <- TRUE

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE, 
  comment = "#>",
  fig.path = "../figures/",
  out.width = "\\textwidth",
   out.extra = "keepaspectratio=true"
)

options(kableExtra.latex.load_packages = FALSE)
library(casebase)
library(colorspace)
library(cowplot)
library(data.table)
library(glmnet)
library(kableExtra)
library(magrittr)
library(pracma)
library(flexsurv) # for fitting gompertz AFT
library(prodlim)
library(riskRegression)
library(splines)
library(survival)
library(tibble)
library(visreg)
library(lubridate)
library(tidyverse)
library(scales)
options(digits = 2, scipen = 999)
# set the seed for reproducible output
set.seed(1234)

eval_introduction <- TRUE
eval_theory <- TRUE
eval_implementation <- TRUE
eval_cs1 <- T
eval_cs2 <- T
eval_cs3 <- T
eval_cs4 <- T
eval_colophon <- TRUE

### 2020-07-28 analysis/paper/paper.tex
extended figure width to match text

{\centering \includegraphics{../figures/plot-stratified-erspc-data-1}

@@

{\centering \includegraphics{../figures/erspc-cox-cif-1}

@@

{\centering \includegraphics{../figures/compPop-1}

@@

{\centering \includegraphics{../figures/bmtcrr-risk-1}

@@

{\centering \includegraphics{../figures/brierpt1-1}

@@

{\centering \includegraphics{../figures/coefplots-1}

@@

{\centering \includegraphics{../figures/riskregressionBrier-1}

@@

\begin{center}\includegraphics{../figures/stanford-poptime-1} \end{center}

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 Model4 
#>    491    459    444    445
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{center}\includegraphics{../figures/stanford-hazard-1} \end{center}

@@

\begin{center}\includegraphics{../figures/stanford-risk-1} \end{center}

@@

\begin{center}\includegraphics{../figures/stanford-1y-haz-1} \end{center}

@@

\begin{CodeOutput}
#>  time     
#>     0 0.00
#>   365 0.72
\end{CodeOutput}

\begin{CodeOutput}
#> [1] 0.65
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{center}\includegraphics{../figures/unnamed-chunk-12-1} \end{center}

@@

This report was generated on 2020-07-28 09:55:47 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> Local:    master /home/jesseislam/Documents/gits/cbpaper
#> Remote:   master @ origin (git@github.com:Jesse-Islam/cbpaper.git)
#> Head:     [d30ba8c] 2020-07-22: Merge pull request #23 from sahirbhatnagar/editMax
\end{CodeOutput}
\end{CodeChunk}

>>>>

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/plot-stratified-erspc-data-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/erspc-cox-cif-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/compPop-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/bmtcrr-risk-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/brierpt1-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/coefplots-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/riskregressionBrier-1}

@@

\begin{center}\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/stanford-poptime-1} \end{center}

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 Model4 
#>    489    457    439    440
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{center}\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/stanford-hazard-1} \end{center}

@@

\begin{center}\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/stanford-risk-1} \end{center}

@@

\begin{center}\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/stanford-1y-haz-1} \end{center}

@@

\begin{CodeOutput}
#>  time     
#>     0 0.00
#>   365 0.74
\end{CodeOutput}

\begin{CodeOutput}
#> [1] 0.67
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{center}\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/unnamed-chunk-12-1} \end{center}

@@

This report was generated on 2020-07-28 10:08:15 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> Local:    master /home/jesseislam/Documents/gits/cbpaper
#> Remote:   master @ origin (git@github.com:Jesse-Islam/cbpaper.git)
#> Head:     [c4450d3] 2020-07-28: Vetted lit-rev, fig and fig comments (cs3)
\end{CodeOutput}
\end{CodeChunk}
